### 2014-03-08 paper/abstract.tex
paper: change tovi color, add lots of text, update routing algorithm

\begin{abstract}
3D printers offer extraordinary flexibilty in prototyping the shape and mechanical function of objects.  However, in spite of recent work, a 3D printer's role in prototyping \emph{interactivity} is still not clear.  While macro-scale digital fabrication devices cannot manufacture electronics in-place, we propose a general technique for redirecting active components through the core and onto the surface of 3D printed interactive objects using a series of tubes.  We describe the design space of tubes and hollow chambers for interaction design: there are a variety of types, topologies, and inserted media for tubes that can be leveraged to create diverse inputs and outputs.  We present a technique and design tool for routing tubes of various topologies through the interior of 3D printed parts.  Our design tool is integrated into a 3D model manipulation program.  There are two distinct routing algorithms.  One allows users to select begin and end points for tubes, then uses A* path routing and physics-based simulation to minimize the bending energy of routed paths.  The second allows users to enter a description of paths to follow: for this we developed a novel neon sign routing algorithm and offer proof of its optimality.  We present several totally tubular prototypes we created using this tool to show its flexibility and potential, as well as to explore new points in the tube design space.
\end{abstract}

>>>>

\begin{abstract}
3D printers offer extraordinary flexibilty in prototyping the shape and mechanical function of objects.  However, in spite of recent work, a 3D printer's role in prototyping \emph{interactivity} is still not clear.  While macro-scale digital fabrication devices cannot manufacture electronics in-place, we propose a general technique for redirecting active components through the core and onto the surface of 3D printed interactive objects using a series of tubes.  We describe the design space of tubes and hollow chambers for interaction design: there are a variety of types, topologies, and inserted media for tubes that can be leveraged to create diverse inputs and outputs.  We present a technique and design tool for routing tubes of various topologies through the interior of 3D printed parts.  Our design tool is integrated into a 3D model manipulation program.  There are two distinct routing algorithms.  One allows users to select begin and end points for tubes, then uses A* path routing and physics-based simulation to minimize the bending energy of routed paths.  The second allows users to enter a description of paths to follow: for this we developed a novel neon sign routing algorithm and offer proof of several key traits.  We present several totally tubular prototypes we created using this tool to show its flexibility and potential, as well as to explore new points in the tube design space.
\end{abstract}

### 2014-03-08 paper/conclusion.tex
paper: change tovi color, add lots of text, update routing algorithm

\section{Conclusion}
In conclusion, tubes are cool.  You can do lots of things with them.  There are different kinds and topologies of tubes.  There are different things you can put in them.  This is cool for makers and also people with really expensive machines.

>>>>

\section{Conclusion}
While today's 3D printers are not yet able to fabricate active components in-place, we suggest that 3D printed interactive devices can be created with redirection of active input and output via tubes.  In addition to describing the design space of tubes and connecting related works created through both traditional processes and rapid prototyping methods, we also presented a design tool for the creation of tubes inside arbitrary 3D models.  We fabricated several example objects using this tool to explore new points in the design space.

We are heartened by our success: it opens new opportunities both for makers with consumer-grade 3D printers and research and industrial labs with higher-end machines.  We are excited to release our tool into the wild and see what people will build.

### 2014-03-08 paper/designspace.tex
note about reference
paper: change tovi color, add lots of text, update routing algorithm

@@

\subsection{Interaction Techniques}
These didn't get discussed yet.
\begin{itemize}
\item \cite{Iwata-volflex} - a display made up of many balloons that inflate and deflate to change the shape
\item \cite{Kim-inflatablemouse} - a basic mouse, but it inflates so you can store it and also use it more reasonably than a flat mouse
\item \cite{Hashimoto-squirming} - hold a speaker in your hands, and air pressure changes make it feel like you're holidng a living, squirming thing
\end{itemize}

@@

Touch sensing is enabled through tubes filled with conductive media.  Traditional wires (threadable) may be used, but we have had success with conductive paint (liquid).  Using conductive paint and Swept Frequency Capacitve Sensing (SFCS \cite{Sato-touche}), an interior star tube topology can enable single-wire touch- and grasp-sensing at any set of points on a printed object's surface (see Figure \cite{fig:toy}).  Simple capacitance measurements are possible using the same media, and custom-designed sensors like those created in Savage, et al.,'s Midas system are also possible \cite{Savage-midas}.

@@

\emph{Visual} outputs can be mediated by gases, liquids, solid, particulates, or threadables.  EL wire can be threaded through custom paths to create neon signs, as in Figure \ref{fig:neon}.  Colored liquids can be mixed and split before exiting an opaque device, or in a transparent device their mixing, splitting, and paths could be used for dispaly.  PneUIs \cite{Yao-pneui} can be fabricated as single parts: the rubberlike material offered by our Objet is inflatable when thin (200\% elongation at break), and a PneUI located at the terminus of a tube could be actuated by a system-side air pump (see Figure \ref{fig:braille}).  Mechanical motion can be mediated through fluids (a light object which is partially contained in a tube or located at its end could be pushed by the fluid pressure of the tube) or threadables (e.g., muscle wire).  Large particles trapped in tubes visible to the user can be used for, e.g., maze games (see Figure \ref{fig:maze}).  Using techniques like those described by Harrison, et al., in \cite{Harrison-buttons}  \valkyrie{this paragraph seems terrible.  I think all these paragraphs might seem terrible...}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{This box (a) contains an enclosed Helmholz resonator, seen in the cutaway view (b).  This resonator creates a sound when air is blown through the tube at the top, because air compresses at the small neck joint between the chamber and the tube.  \valkyrie{need to get a test print of this that actually works}}
\label{fig:embeddedcomponents}
\end{figure}

\emph{Haptic} outputs are possible through compressible and incompressible fluids.  Fluids can actuate particulates and create programmable pliability (as discussed above and in \cite{Follmer-jamming}).  Additionally, use of semi-closed tubes with rubberlike material as the caps allows for gases to actuate surface features (see Figure \ref{fig:braille}).  Sodhi, et al., in \cite{Sodhi-aireal} created free-air haptic feedback using controlled vortex generation: this technique could also be reproduced using a series of tubes.

@@

Both identification by recall and intentional encoding are possible.  As seen in \cite{Ono-touchandactivate}, different objects have different acoustic signatures.  Additionally, two objects that are visually identical but which have fully enclosed (or other types) of tubes on their interior can be distinguised acoustically.  Thus we can recall an object's identity once its acoustic signature has been recorded.

>>>>

\subsubsection{Dimensions of Tubes}

\valkyrie{Reference those pages from Bjoern: http://ttb.com/recent-news/diagrams/ We can talk about wall thickness, tangent length, degree of bend, arg bend angle, inner and outer diameters, centerline radius, etc.}

@@

@@

Touch sensing is enabled through tubes filled with conductive media.  Traditional wires (threadable) may be used, but we have had success with conductive paint (liquid).  Using conductive paint and Swept Frequency Capacitive Sensing (SFCS \cite{Sato-touche}), an interior star tube topology can enable single-wire touch- and grasp-sensing at any set of points on a printed object's surface (see Figure \cite{fig:toy}).  Simple capacitance measurements are possible using the same media, and custom-designed sensors like those created in Savage, et al.,'s Midas system are also possible \cite{Savage-midas}.

@@

\emph{Visual} outputs can be mediated by gases, liquids, solid, particulates, or threadables.  EL wire can be threaded through custom paths to create neon signs, as in Figure \ref{fig:neon}.  Colored liquids can be mixed and split before exiting an opaque device, or in a transparent device their mixing, splitting, and paths could be used for display.  PneUIs \cite{Yao-pneui} can be fabricated as single parts: the rubberlike material offered by our Objet is inflatable when thin (200\% elongation at break), and a PneUI located at the terminus of a tube could be actuated by a system-side air pump (see Figure \ref{fig:breathe}).  Mechanical motion can be mediated through fluids (a light object which is partially contained in a tube or located at its end could be pushed by the fluid pressure of the tube) or threadables (e.g., muscle wire).  Large particles trapped in tubes visible to the user can be used for, e.g., maze games (see Figure \ref{fig:maze}).  Using techniques like those described by Harrison, et al., in \cite{Harrison-buttons}  \valkyrie{this paragraph seems terrible.  I think all these paragraphs might seem terrible...}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{This box (a) contains an enclosed Helmholz resonator, seen in the cutaway view (b).  This resonator creates a sound when air is blown through the tube at the top, because air compresses at the small neck joint between the chamber and the tube.  \valkyrie{need to get a test print of this that actually works}}
\label{fig:ocarina}
\end{figure}

\emph{Haptic} outputs are possible through compressible and incompressible fluids.  Fluids can actuate particulates and create programmable pliability (as discussed above and in \cite{Follmer-jamming}).  Additionally, use of semi-closed tubes with rubberlike material as the caps allows for gases to actuate surface features (see Figure \ref{fig:breathe}).  Sodhi, et al., in \cite{Sodhi-aireal} created free-air haptic feedback using controlled vortex generation: this technique could also be reproduced using a series of tubes.  Iwata, et al., explored volumetric fluid-based interactions with programmatically inflatable balloons and an overhead projector in \cite{Iwata-volflex}, and additionally haptic outputs can be used to increase ergonomics, as in the inflatable mouse by Kim, et al. \cite{Kim-inflatablemouse}.

@@

Both identification by recall and intentional encoding are possible.  As seen in \cite{Ono-touchandactivate}, different objects have different acoustic signatures.  Additionally, two objects that are visually identical but which have fully enclosed (or other types) of tubes on their interior can be distinguished acoustically.  Thus we can recall an object's identity once its acoustic signature has been recorded.

### 2014-03-08 paper/exampleobjects.tex
paper: change tovi color, add lots of text, update routing algorithm

\subsection{Touch-sensitive Toy}

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{A touch-sensitive rabbit whose tubes are filled with conductive paint.  Sensing is done on a single wire via SFCS.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:toy}
\end{figure}

We created a touch-sensitive toy and an app that goes along with it, reminiscent of the boat application in \cite{Harrison-acoustic}.  This toy has an interior star topology where a single wire attached to an Arduino running an SFCS sketch splits to connect to sensors on the eyes, ears, tail, and nose.  To accompany this toy, we built an app which prompts the user to find and touch certain parts of the animal (see Figure \ref{fig:toy}).

\subsection{Braille Haptic Display}

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{When air pressure is changed in the six tubes, their caps inflate or deflate. Through controlled actuation, we can create Braille letters.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:braille}
\end{figure}

Using a $2\times3$ array of semi-closed tubes, we created a Braille output interface.  The closed ends of the tubes are covered in a rubberlike material, while on the system side the tubes are attached to individually-controlled air pumps.  These pumps can create positive or negative pressure in each tube, pushing the cap up or down and rendering a tactile Braille letter when used in concert (see Figure \ref{fig:braille}).

@@

A custom ``radio'' built using tubes allows users to tune to different stations and play sound files related to those stations.  This device uses a network of disconnected open tubes filled with conductive paint to connect traditional electronic components (a potentiometer, a piezo, and an LED) to a microcontroller.

@@

Our presence-aware pen holder can distinguish which tool or tools a user has picked up (see Figure \ref{fig:pens}).  Such information was used by \cite{Mueller-constructable} to determine which physical laser pointer a designer was using to interact with their interface.  Our pen holder uses the FlyEye technique described by Wimmer in \cite{Wimmer-flyeye} and contains open tubes filled with fiber optic cables, two per pen chamber.  One tube from each chamber leads to an infrared LED, and the other leads to a camera.  When a pen is in its appointed place, light from the LED is reflected off its bottom and travels through the other optical fiber into the camera, where it registers as a bright point.  A dark point on the camera region appears when a pen has been removed from its place, and the position of the point indicates which pen it is.

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{A neon sign (a) and its partial duplicate designed using our tool (b).  (c) shows the selections we made to generate our tube structures.  (d) shows the internal structure of the tubes generated by our design tool.}
\label{fig:neon}
\end{figure}

Neon art, perhaps best known for its association with Las Vegas, is traditionally made from hand-formed glass tubes containing neon gas.  The tubes light up when a current is passed through them.  For this type of art, the path of the tubes is of crucial importance, as it determines how the sign will look.  We designed a partial duplicate of a renowned piece of neon art from Seattle (or was it Portland?).  The piece features open tubes due to support-flushing constraints, however the tubes could also be semi-closed.  They have been threaded with EL wire which is lit in sequence to create an animation.

>>>>

\subsection{Touch-sensitive Toys}

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{A touch-sensitive brain whose tubes are filled with conductive paint.  Sensing is done on a single wire via SFCS.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:toy}
\end{figure}

We created a set of touch-sensitive toys and a companion app, reminiscent of the boat application in \cite{Harrison-acoustic}.  The brain, rabbit, and boat each have several distinct touch points on their surfaces.  These touch points are connected by an interior star topology of tubes filled with conductive copper paint, and touch sensing is performed via a single wire and SFCS (see Figure \ref{fig:toy}).  We built a smart base which can distinguish between the toys and also determine which toy is mounted: since each toy and each gesture has a distinct capacitive signature, we use a simple classifier trained to detect both toy and gesture based on profile.  These devices were all fabricated on a Makerbot Replicator 2.

\subsection{Breathing Bunny}

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{This rabbit has an open tube leading to its mouth and a semi-closed tube capped with flexible material in its back.  When air is sucked in through the open tube, the back becomes stiff as though the rabbit has breathed in.}
\label{fig:breathe}
\end{figure}

We created a rabbit with a pair of tubes that can simulate breathing (see Figure \ref{fig:breathe}).  For this, we used a combination air/vacuum pump: one terminal creates a vacuum while the other creates positive pressure.  Our rabbit has two tubes, one open tube exiting at its mouth and one semi-closed tube capped with rubberlike material in its abdomen.  We connected one tube to each of our pump's terminals, and using a programmable power supply we can mimic a rabbit's breathing pattern.  This example was printed on our Objet Connex 260. \valkyrie{this paragraph is really unclear}

@@

A custom radio built using tubes allows users to tune to different stations and listen in.  This device uses a network of disconnected open tubes filled with conductive paint to connect traditional electronic components (two potentiometers, a speaker, and an LED) to a microcontroller.  We hid the microcontroller and a battery-driven power supply in the base of the radio to make it portable.  We fabricated this device on our Makerbot Replicator 2.

@@

Our presence-aware pen holder can distinguish which tool or tools a user has picked up (see Figure \ref{fig:pens}).  Such information was used by \cite{Mueller-constructable} to determine which physical laser pointer a designer was using to interact with their interface.  Our pen holder uses the FlyEye technique described by Wimmer in \cite{Wimmer-flyeye} and contains open tubes filled with fiber optic cables, two per pen chamber.  One tube from each chamber leads to an infrared LED, and the other leads to a camera.  When a pen is in its appointed place, light from the LED is reflected off its bottom and travels through the other optical fiber into the camera, where it registers as a bright point.  A dark point on the camera region appears when a pen has been removed from its place, and the position of the point indicates which pen it is.  This prototype was built by our Objet Connex 260.

\subsection{Maze}

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{Our maze game has a large single particle trapped inside a fully enclosed tube.  It offers hours of fun!}
\label{fig:maze}
\end{figure}

We created a maze game with a single particle trapped in a fully enclosed tube.  To fabricate the tube, we created it in two halves that were fastened together via glue, due to limitations in our ability to remove support material otherwise.  We created this prototype on our Makerbot Replicator 2.

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{A two-state animated neon sign designed using our tool (a)(b) \valkyrie{Tovi: we could use your PDF has to make this animate in place :)}.  (c) shows the SVG input files to create this sign, and (d) shows an isometric view of the tubes created by our tool.}
\label{fig:neon}
\end{figure}

Neon art, perhaps best known for its association with Las Vegas, is traditionally made from hand-formed glass tubes containing neon gas.  The tubes light up when a current is passed through them.  For this type of art, the path of the tubes is of crucial importance, as it determines how the sign will look.  We designed a custom neon sign bearing the UIST logo and the waves of Hawaii.  The piece features open tubes due to support-flushing constraints, however the tubes could also be semi-closed.  They have been threaded with EL wire which is lit in sequence to create an animation.  Our sign was fabricated on the Objet Connex 260.

### 2014-03-08 paper/introduction.tex
paper: change tovi color, add lots of text, update routing algorithm

Willis, et al., ``envision a future world where interactive devices can be printed rather than assembled; a world where a device with active components is created as a single object, rather than a case enclosing circuit boards and individually assembled parts" \cite{Willis-printedoptics}.  This is a vision we eagerly share: 3D printers are capable of greating arbitrary geometries not feasible to manufacture using traditional processes, and we see these capabilities being underutilized by makers and designers.  We see many opportunitities to increase the interactivity of 3D prints using today's printer technology.
\tovi{Might want some examples of what possibilities this opens up}

>>>>

Willis, et al., ``envision a future world where interactive devices can be printed rather than assembled; a world where a device with active components is created as a single object, rather than a case enclosing circuit boards and individually assembled parts" \cite{Willis-printedoptics}.  This is a vision we eagerly share: 3D printers are capable of creating arbitrary geometries not feasible to manufacture using traditional processes, and we see these capabilities being underutilized by makers and designers.  We see many opportunities to increase the interactivity of 3D prints using today's printer technology.
\tovi{Might want some examples of what possibilities this opens up}

### 2014-03-08 paper/limitations.tex
paper: change tovi color, add lots of text, update routing algorithm

The physical fabrication process also leads to some considerations.  To print without support on a hobbyist machine, internal tubes cannot have overhangs of greater than $45^{\circ}$.  On the Objet, support-free prints cannot overhang more than $14^{\circ}$.  Removal of support from printed tubes can be complicated, especially when their internal geometry and branching structures are complex.

Our design tool is not yet fully capable of realizing all possibilities in the design space of tubes.  It lacks X and Y \valkyrie{probably it will lack the network manipulation to make mixing or splitting tubes...?}.  We hope to address this in future work.

>>>>

The physical fabrication process also leads to some considerations.  To print without support on a hobbyist machine, internal tubes cannot have overhangs of greater than $45^{\circ}$.  On the Objet, support-free prints cannot overhang more than $14^{\circ}$.  Removal of support from printed tubes can be troublesome, especially when their internal geometry and branching structures are complex.

Our design tool is not yet fully capable of realizing all possibilities in the design space of tubes.  It lacks X and Y \valkyrie{probably it will lack the network manipulation to make mixing or splitting tubes...?}.  Additionally, as mentioned there are opportunities to improve the algorithm for neon sign routing, as ours does not guarantee a shortest-path routing.  We hope to address this in future work.

### 2014-03-08 paper/relatedwork.tex
update of algorithm text
paper: change tovi color, add lots of text, update routing algorithm

Previous work has investigated the integration of interactivity into the fabrication process.  \cite{Willis-printedoptics} used light pipes, solid clear tubes, to create integrated displays.  \cite{Savage-sauron} investigated the use of computer vision to track interactions with physical mechanisms.
\begin{itemize}
\item \cite{Savage-sauron} - Sauron.  computer vision of mechanical components obviates electronics installation.
\item \cite{Willis-printedoptics} - Printed Optics.  doing cool stuff with clear material (touch sensing and display)
\item \cite{Slyper-pressure} - robots that are made of squishy stuff where air pressure changes are sensed.  input components designed to react to different manipulations (pushing, squeezing, twisting, etc.)
\item \cite{Navarrette-gps} - I'm a little unclear on what they did, but they fabbed something with a "3D circuitboard" that has a bypass that goes into 3D.  they don't offer a routing algorithm or anything, though.
\item \cite{Sarik-tracebrush} - this uses an airspray machine to add conductive paths to surface of 3D prints
\item \cite{Optomec} - fancy machines that spray conductive film
\item \cite{Sells-reprap} - the RepRap people using a syringe of hot solder to squirt flat circuits into flat channels
\item \cite{icecats-conductivepaint} - an instructable I followed to make my first batch of conductive paint
\end{itemize}

\subsection{Routing}
\begin{itemize}
\item \cite{Savage-midas} - Midas.  routing in 2D to connect up capacitive sensors
\item \cite{Park-microchannels} - similar to injection of liquid metal, above
\item \cite{Majidi-curvature} - inject liquid metal into really thin tubes in a soft substrate, sense stretching by changing resistance

Our neon routing algorithm is similar to that described by Wong, et al., in \cite{Wong-continuousline}.  However, We are not confined to the plane to avoid line-crossings, and we also have additional freedom in creating lines where none existed.  Because we can shield neon post-print with black tape or material (thus rendering it invisible), we don't have the same need to avoid drawing new line segments, and we are free to create much shorter paths.  It's not quite a TSP
\end{itemize}

>>>>

Previous work has investigated the integration of interactivity into the fabrication process.  \cite{Willis-printedoptics} used light pipes, solid clear tubes, to create integrated displays: our work allows a superset of these capabilities, and Printed Optics is a part of our design space.  \cite{Savage-sauron} investigated the use of computer vision to track interactions with physical mechanisms.  Using tubes for redirection, it is possible to replicate these mechanically sensitive techniques (see Figure \ref{fig:pens}), however our work does not focus on computer vision alone.  Slyper, et al., \cite{Slyper-pressure} 3D printed flexible robot armatures capable of sensing interaction via changes in air pressure.  This technique is complementary to ours, as we allow for placing these interactive elements anywhere on an object's surface while they had to place them in locations accessible for electronics insertion.

Other research has attempted to bring traditional electronics to 3D prints, either on the surface or via interior channels.  Sells, et al., in \cite{Sells-reprap} create channels on the surface of a 3D printed object which are filled with a special computer-controlled syringe of liquid solder to create connections.  Their focus is on creating self-replicating 3D printers, and their electronics are combined to traditional 2D routed circuitboards.  Sarik, et al., \cite{Sarik-tracebrush} \valkyrie{I never found a real paper of this.  The Microsoft website has a "print" of it with TEI boilerplate, but I couldn't find it in the digital library.  What's up with that?} and the Optomec company \cite{optomec} both created techniques for taking an already-printed object and spraying conductive material onto its surface.  In contrast, our technique can lead to more durable circuitry, since it is routed through the core of the object rather than on its surface.  Navarette, et al., in \cite{Navarrette-gps} created a functioning GPS whose circuit routing extended into true 3D (as compared to the 2.5D boards created by stacking traditional 2D circuitboards).  However, they created this one-off routing by hand and do not offer any general algorithms or techniques.  In the area of robotics, softer-than-skin interactive surfaces have been created using tubed interfaces fabricated from silicone molds.  \cite{Park-microchannels} and \cite{Majidi-curvature} use microchannels filled with liquid metal for pressure or curvature sensing: the metal in the channels changes resistance as the channels are stretched.
\begin{itemize}
\item \cite{icecats-conductivepaint} - an instructable I followed to make my first batch of conductive paint
\end{itemize}

\subsection{Routing}

Part of our contribution is in the algorithms and techniques used for routing tubes through 3D objects.

General-purpose routing for connecting 2D capacitive sensors to terminals is discussed in \cite{Savage-midas}.  These techniques, based on circuitboard routing, are limited to planar and unfoldable shapes, and are intended for use on the surface of objects rather than through their cores.

Similar to our neon-sign routing algorithm, Wong presents a graph-based approach for generating continuous line illustrations from images \cite{Wong-continuousline}. Its approach of linking edges into a continuous line based on semi-Eulerization is similar to ours.  However, we are not confined to the plane to avoid line-crossings, and we have additional freedom in creating invisible lines where none existed.  This is possible for us thanks to \emph{blocking out}\footnote{In neon sign making, segments of a tube that should not appear illuminated are covered with opaque paint. This is called "blocking out".\url{http://en.wikipedia.org/wiki/Neon_sign}}. Prior work used tours of nodes, rather than edges, and cast continuous line drawing as a traveling salesman problem~\cite{Bosch-tsp}.  Schweikardt, et al., also made a connection between electroluminescent wire and graph theory, though their contribution is orthogonal to ours: they provide a tangible construction kit with smart nodes for building physical graph examples \cite{Schweikardt-tei09}. Edges are lit by EL wire.

\subsection{Misc}
\bjoern{These may not belong in related work, but I'm just collecting them here.}
\begin{itemize}
\item \cite{strattman1997neon} - Strattman is the standard "text book" for neon lighting designers.
\end{itemize}

### 2014-03-08 paper/tubes.tex
paper: change tovi color, add lots of text, update routing algorithm

\section{A Series of Tubes}

\section{Tool for Tube Design}

We created a tool which novice designers can use to create tube-powered interfaces in arbitrary 3D models.  This tool allows users to brush over the surface of their model to either select exterior connection points of their tubes (see Figure \ref{fig:tool-process-interior}) or to author the tubes' interior paths (see Figure \ref{fig:tool-process-exterior}).  Once the user's selections are made, we create a complete routing using either the exterior connection point method (A*) or the interior path method (graph edge creation, Euler circuit generation).  We thicken our routing and use a physics-based rod simulation to minimize bending energy of tubes.  We also apply templates where appropriate (e.g., 3D cross-overs for tubes that intersect).  The resultant routing is subtracted from the user's mesh.  The modified mesh can then be 3D printed.

@@

our tool creates an initial shortest-path routing using A* to estimate the routed distance between points.  This routing is used to create a rod; we run physics-based simulation steps on the rod to minimize its bending energy (and thereby minimize the bend radius of the tubes).

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{This figure has several sub-figures.  a) shows a model with exterior connection points brushed.  b) shows initial routing with A*.  c) shows our physics-based, energy-minimizing rod/tube, d) shows the printed object with the tube (with something in it, copper paint presumably)}
\label{fig:tool-process-exterior}
\end{figure}

@@

How does it actually work?

@@

Collision detection

@@

take into account bend radius of desired material - no need, we just do the minimum-bending path

 (as the edges of the graph are the lines the user wishes to have lit)

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{This figure has several sub-figures.  a) shows an SVG file with some line art  b) highlights the points which can't be tubed as drawn (if they are not connected, of odd degree, etc.).  c) shows our connected graph, d) shows our routing e) shows a printed thing with that kind of tube filled with EL wire}
\label{fig:tool-process-interior}
\end{figure}

This is a relaxed version of the Chinese Postman Problem\footnote{\url{http://en.wikipedia.org/wiki/Route_inspection_problem}}, in which we wish to traverse all edges of the graph described in the user's input with a single Euler circuit, much as a postman needs to walk along every road at least once to deliver mail.  We call our relaxation the Spiderman Postman Problem: we allow the creation of non-existing paths (i.e., the postman may traverse buildings in addition to roads).  If inputted path components are disconnected, we must create edges that connect them; additionally we can create new edges connecting odd-degree vertices rather than simply retracing existing edges.  In the final artifact, all created edges will be shielded by dark material so the inserted medium is not visible (see Figure \ref{fig:tool-process-interior}).

@@

We need to connect disconnected subgraphs in $G$.  Let $G_{dis} = \{G_1, G_2, ... G_n\} \in G$ s.t. $\cup{\{G_i \in G_{dis}\}} = G$ and $G_i \cap G_j  = \{ \} \forall G_i, G_j \in G_{dis}, i\neq j$ be disconnected subgraphs in G.  Create $E_{conn} = \{e = (u, v), u \in G_i, v \in G_j, i \neq j, weight(e) = distance(u, v)\}$ be a set of edges.  Sort $E_{conn}$ s.t. $E_{conn} = \{e_1, e_2, ... e_n\}, weight(e_1) \leq weight(e_2) \leq \ldots \leq weight(e_n)$.  Let $E_{conn-min} = \{ \}$. \valkyrie{another approach to this that actually would minimize it is to reduce each disconnected subgraph to a single point with one edge going to each other disconnected subgraph-point.  these edges' weights would be the lowest weight of any edge connecting any points in the two subgraphs.  by finding a minimum matching on these subgraph points, I think we will get the best answer.}

Beginning with $e_1$, add the first edge $e_i \in E_{conn}$ to $E_{conn-min}$.  Then let $E_{dupe} = \{ e = (u, v) \in E_{conn}$ s.t. $u$  is reachable from $v$ along edges $E' \cup E_{conn-min}$.  Let $E_{conn} = E_{conn} \setminus E_{dupe}$.  Repeat until $E_{conn} = \{ \}$.  Let $E' = E' \cup E_{conn-min}$.

At this stage, we want an Eulerian graph: i.e., we need every vertex to be of even degree.  Let $V_{odd} = \{ v \in V s.t. degree(v) \% 2 = 1 \}$.  Create $E_{circuit} = V_{odd} \times V_{odd}$, s.t. $\forall e=(u,v) \in E_{circuit}, weight(e) = distance(u, v)$.  Find minimum matching $E_{circuit-min} \subseteq E_{circuit}$.  Let $E' = E \cup E_{circuit-min}$.

@@

How we actually cut stuff and make tubes happen.

>>>>

\section{A Series of Tubes - A Tool for Tube Design}

We created a tool which makers can use to create tube-powered interfaces in arbitrary 3D models.  This tool allows designers to brush over the surface of their model to select exterior connection points of their tubes (see Figure \ref{fig:tool-process-interior}) or to import vector art describing the tubes' interior paths (see Figure \ref{fig:tool-process-exterior}).  Once the user's selections are made, we create a complete routing using either the exterior connection point method (A*) or the interior path method (graph edge creation, Euler circuit generation).  We thicken our routing and use a physics-based rod simulation to minimize bending energy of tubes.  We also apply templates where appropriate (e.g., 3D cross-overs for tubes that intersect in the plane).  The resultant routing is subtracted from the original mesh.  The modified mesh can then be 3D printed.

Our tool is implemented as a part of Meshmixer, a consumer mesh editing tool, in C++.

@@

Our tool creates an initial shortest-path routing using A* to estimate the routed distance between points.  This routing is used to create a rod; we run physics-based simulation steps on the rod to minimize its bending energy (and thereby minimize the bend radius of the tubes).

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{An example mesh with exterior connection points brushed (a), and the initial A* routing generated (b).  Our physics-based, energy-minimizing rod/tube at rest (c) and after simulation (d).  (e) shows the complete printed object.}
\label{fig:tool-process-exterior}
\end{figure}

@@

How does it actually work? \valkyrie{Ryan?}

@@

In order to force our simulated rods away from the surface of the mesh, we create ``wind'' pushing inward from the exterior of the mesh.  This wind pushes the tube away from the surface.

\subsubsection{Tubes with Multiple Endpoints}

To allow designers to create tubes with multiple endpoints (like the star topologies in Figure \ref{fig:toys}), we ....???? \valkyrie{create 0-size mesh points in the center of the object, to which we attach one end of every tube?}

@@

A user can import a vector graphics file (such as SVG) describing the path she desires for her tubes.  We create a graph based on this input data, then add edges to make it connected and semi-Eulerian.  We create an Euler tour on the graph, and then thicken the path to create tubes.  Templates are used to resolve tube crossings in the plane.

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{An input vector graphics file (a) and the points which cannot be tubed as drawn (b).  The connected graph created by our software (c) and the resulting Euler circuit (d) permit creation of a novel neon sign (e).}
\label{fig:tool-process-interior}
\end{figure}

The interior path routing problem is a version of the Chinese Postman Problem\footnote{\url{http://en.wikipedia.org/wiki/Route_inspection_problem}}, in which we wish to traverse all edges of the graph described in the user's input with a single Euler circuit, much as a postman needs to walk along every road at least once to deliver mail.  We call our relaxation the Spiderman Postman Problem: we allow the creation of non-existing paths (i.e., the postman may traverse buildings in addition to roads).  If inputted path components are disconnected, we must create edges that connect them; additionally we can create new edges connecting odd-degree vertices rather than simply retracing existing edges.  In the final artifact, all created edges will be blocked out by dark material so the inserted medium is not visible (see Figure \ref{fig:tool-process-interior}).

@@

We need to connect disconnected subgraphs in $G$.  Let $G_{dis} = \{G_1, G_2, ... G_n\} \in G$ s.t. $\cup{\{G_i \in G_{dis}\}} = G$ and $G_i \cap G_j  = \{ \} \forall G_i, G_j \in G_{dis}, i\neq j$ be disconnected subgraphs in G.  Create $E_{conn} = \{e = (u, v), u \in G_i, degree(u)\%2 = 1, v \in G_j, degree(v) \%2 = 1 i \neq j, weight(e) = distance(u, v)\}$ be the set of all edges connecting odd-degree points in two distinct disconnected subgraphs.  To keep only the most desirable edges in $E_{conn}$, contract each subgraph $G_i$ to a single point $u_i$ with the shortest outgoing edges to each other subgraph: $E_{conn} = \cup_{G_i \in G_{dis}} \{e=(u_i, v), v \in G_j,$ s.t. $\forall E_{conn} \ni e_k = (u, v), u \in G_i, v \in G_j, weight(e_k) \geq weight(e)\}$.  Sort $E_{conn}$ s.t. $E_{conn} = \{e_1, e_2, ... e_n\}, weight(e_1) \leq weight(e_2) \leq \ldots \leq weight(e_n)$.

Let $E_{conn-min} = \{ \}$.  Beginning with $e_1$, add the first edge $e_i \in E_{conn}$ to $E_{conn-min}$.  Then let $E_{dupe} = \{ e = (u, v) \in E_{conn}$ s.t. $u$  is reachable from $v$ along edges $E' \cup E_{conn-min}$.  Let $E_{conn} = E_{conn} \setminus E_{dupe}$.  Repeat until $E_{conn} = \{ \}$.  Let $E' = E' \cup E_{conn-min}$.

At this stage, we want an Eulerian graph: i.e., we need every vertex to be of even degree.  Let $V_{odd} = \{ v \in V$ s.t. $degree(v) \% 2 = 1 \}$.  Create $E_{circuit} = V_{odd} \times V_{odd}$, s.t. $\forall e=(u,v) \in E_{circuit}, weight(e) = distance(u, v)$.  Find minimum matching $E_{circuit-min} \subseteq E_{circuit}$.  Let $E' = E \cup E_{circuit-min}$.

@@

How we actually cut stuff and make tubes happen. \valkyrie{Ryan?}
